Towards open collaboration in biomedical and health research: A protocol for a scoping review of open collaboration

### 2025-01-08 doc/paper.qmd

---
title: "Towards open collaboration in biomedical and health research: An open collaborative scoping review"
date: last-modified
author: 
  - name: Hannah Chatwin
    affiliations: 
      - ref: au
  - name: Mario Garcia
    affiliations: 
      - ref: ku
  - name: Daniel B. Ibsen
    affiliations: 
      - ref: sdca
      - ref: au
  - name: Luke W. Johnston
    affiliations: 
      - ref: sdca
      - ref: au
affiliations:
  - id: sdca
    name: Steno Diabetes Center Aarhus
    country: Denmark
  - id: au
    name: Aarhus University
    country: Denmark
  - id: ku
    name: Copenhagen University
    country: Denmark
format: html
bibliography: references.bib
csl: vancouver.csl
---

```{r setup}
#| include: false
knitr::opts_chunk$set(echo = FALSE)
library(stringr)
library(here)
source(here("R/openalex-search.R"))
# TODO: This doesn't work, Luke is fixing it in connection with making Quarto website
# search_terms_inline <- str_replace_all(search_terms$general, "\\*", "\\\\\\*")
```

@@

Interestingly, the level of organization with most papers is the multi-center level with two papers from ManyPrimates et al (ManyPrimates 2019 and ManyPrimates 2021) and Grange et al. In this organization level the most urgent needs are: 1) identifying the needs for open collaboration and 2) creating an infrastructure that allows those needs to be satisfied. Indeed, Grange et al describes a systematic review as an exploration of the needs for 11 UKRN centers to implement open collaborative practives. In this paper they specially focus on tools and resources among the 11 institutions and make clear the need for starting to utilize open resources as a first step to adapt open collaborative practices. The first paper from ManyPrimates et al [REF] describes the start of another multi-center collaboration, albeit from different institutions. It is interesting to observe that in this situation, the complex issue is to start the collaboration itself, which was ignited thanks to a symposium and an email chain among future collaborators. In contrast, ManyPrimates could quickly develop an open collaborative structure with relative ease in comparison to changing an already solid infrastructure, like in the case of Grange et al.

@@

## Discussion

>>>>

---
title: "Towards open collaboration in biomedical and health research: An open collaborative scoping review"
date: last-modified
author:
  - name: Mario Garcia
    affiliations:
      - ref: ku
  - name: Daniel B. Ibsen
    affiliations:
      - ref: sdca
      - ref: au
  - name: Luke W. Johnston
    affiliations:
      - ref: sdca
      - ref: au
affiliations:
  - id: sdca
    name: Steno Diabetes Center Aarhus
    country: Denmark
  - id: au
    name: Aarhus University
    country: Denmark
  - id: ku
    name: Copenhagen University
    country: Denmark
---

```{r setup}
#| include: false
knitr::opts_chunk$set(echo = FALSE)
library(stringr)
library(here)
source(here("R/openalex-search.R"))
search_terms_inline <- glue::glue("({search_terms()$title_search}[title]) AND {search_terms()$general_search}")
```

@@

Interestingly, the level of organization with most papers is the
multi-center level with two papers from ManyPrimates et al (ManyPrimates
2019 and ManyPrimates 2021) and Grange et al. In this organization level
the most urgent needs are: 1) identifying the needs for open
collaboration and 2) creating an infrastructure that allows those needs
to be satisfied. Indeed, Grange et al describes a systematic review as
an exploration of the needs for 11 UKRN centers to implement open
collaborative practives. In this paper they specially focus on tools and
resources among the 11 institutions and make clear the need for starting
to utilize open resources as a first step to adapt open collaborative
practices. The first paper from ManyPrimates et al \[REF\] describes the
start of another multi-center collaboration, albeit from different
institutions. It is interesting to observe that in this situation, the
complex issue is to start the collaboration itself, which was ignited
thanks to a symposium and an email chain among future collaborators. In
contrast, ManyPrimates could quickly develop an open collaborative
structure with relative ease in comparison to changing an already solid
infrastructure, like in the case of Grange et al.

@@

### 2025-01-08 doc/protocol.qmd

This is a scoping review, so we are following the framework described by
Arksey and O'Malley
([DOI:10.1080/1364557032000119616](https://doi.org/10.1080/1364557032000119616))
and by Levac, Colquhoun, and O'Brien
([DOI:10.1186/1748-5908-5-69](https://doi.org/10.1186/1748-5908-5-69))
as well as the guidelines outlined in the PRISMA-ScR
([DOI:10.7326/M18-0850](https://doi.org/10.7326/M18-0850) statement.

>>>>

This is a scoping review, so we are following the framework described in
[@Arksey2005, @Levac2010] as well as the guidelines outlined in the
PRISMA-ScR statement [@Tricco2018].
